### 2022-07-19 Papers/ICCC-2023/sections/design.tex
design

\section{Language and compiler design}

@@

@@

>>>>

\section{Language and compiler design}
\label{language-compiler-design}

@@

In the CTFE First approach, frontend serves the same role of constructing the programs intermidiate representation, as in conventional compilers \cite{puntambekar:compiler_design}.

@@

CTFE First does not put any additional requierments on compiler backend.
When using this pattern, an out-of-the-box backend library, can be used, as was the case with C-=-1 compiler.

The backend code must be invokable from within the interpreted program in the target language.
Depending on how the interpreter was designed, this can represent a significant undertaking.
Compiler backends are large and for the Compiler Interface to take advantage of them fully, they must be fully available.
This means exposing each function and type within the library, to the interpreted code.
These bindings could feasibly be generated automatically \cite{marshalling_auto_generation}, but this tehnique was not used when implementing C-=-1 compiler.
